\section*{}
\addcontentsline{toc}{section}{References}
\label{chap:references}
\begin{thebibliography}{99}
\bibitem{RFC723x}
RFC7230 Fielding, R., Ed., and J. Reschke, Ed., "Hypertext Transfer Protocol (HTTP/1.1): Message Syntax and Routing", RFC 7230, June 2014, Available at:http://www.rfc-editor.org/info/rfc7230  [Accessed 26 Mar. 2015]. \\
RFC7231 Fielding, R., Ed., and J. Reschke, Ed., "Hypertext Transfer Protocol (HTTP/1.1): Semantics and Content", RFC 7231, June 2014, Available at: http://www.rfc-editor.org/info/rfc7231 [Accessed 26 Mar. 2015]. \\
RFC7232 Fielding, R., Ed., and J. Reschke, Ed., "Hypertext Transfer Protocol (HTTP/1.1): Conditional Requests", RFC 7232, June 2014, Available at: http://www.rfc-editor.org/info/rfc7232 [Accessed 26 Mar. 2015]. \\ 
RFC7233 Fielding, R., Ed., Lafon, Y., Ed., and J. Reschke, Ed., "Hypertext Transfer Protocol (HTTP/1.1): Range Requests", RFC 7233, June 2014, Available at: http://www.rfc-editor.org/info/rfc7233 [Accessed 26 Mar. 2015]. \\
RFC7234 Fielding, R., Ed., Nottingham, M., Ed., and J. Reschke, Ed., "Hypertext Transfer Protocol (HTTP/1.1): Caching", RFC 7234, June 2014, Available at: http://www.rfc-editor.org/info/rfc7234 [Accessed 26 Mar. 2015]. \\
RFC7235 Fielding, R., Ed., and J. Reschke, Ed., "Hypertext Transfer Protocol (HTTP/1.1): Authentication", RFC 7235, June 2014, Available at: http://www.rfc-editor.org/info/rfc7235 [Accessed 26 Mar. 2015].
\bibitem{http2}
Hypertext Transfer Protocol version 2 (draft-ietf-httpbis-http2-17) (2015). M. Belshe, Twist R. Peon [online] IETF, Available at:
https://datatracker.ietf.org/doc/draft-ietf-httpbis-http2/?include\_text=1 [Accessed 26 Mar. 2015].
 \bibitem{hpack}
HPACK - Header Compression for HTTP/2 draft-ietf-httpbis-header-compression-07 (2015). R. Peon,  H. Ruellan [online] IETF, Available at: http://tools.ietf.org/html/draft-ietf-httpbis-header-compression-07 [Accessed 26 Mar. 2015].
\bibitem{stenberg}
Stenberg, D. (2015). http2 explained - The HTTP/2 book. [online] Daniel.haxx.se. Available at: http://daniel.haxx.se/http2/ [Accessed 27 Mar. 2015].
\bibitem{httpbis}
Tools.ietf.org, (2015). Httpbis Status Pages. [online] Available at: https://tools.ietf.org/wg/httpbis/ [Accessed 27 Mar. 2015].
\bibitem{spdy}
Google Developers, (2015). SPDY. [online] Available at: https://developers.google.com/speed/spdy/ [Accessed 27 Mar. 2015].
\bibitem{raymond}
Raymond, E. (2015). The Importance of Being Textual. [online] Catb.org. Available at: http://www.catb.org/esr/writings/taoup/html/ch05s01.html [Accessed 27 Mar. 2015].
\bibitem{curlhttp2}
Curl.haxx.se, (2015). cURL - README.http2. [online] Available at: http://curl.haxx.se/dev/readme-http2.html [Accessed 27 Mar. 2015].
\bibitem{wiresharkhttp2}
Wiki.wireshark.org, (2015). HTTP2 - The Wireshark Wiki. [online] Available at: https://wiki.wireshark.org/HTTP2 [Accessed 27 Mar. 2015].
\bibitem{breach}
Breachattack.com, (2015). BREACH ATTACK. [online] Available at: http://breachattack.com/ [Accessed 27 Mar. 2015].
\bibitem{crime}
Blackhat, (2013). A Perfect CRIME?. [online] Available at: https://media.blackhat.com/eu-13/briefings/Beery/bh-eu-13-a-perfect-crime-beery-wp.pdf [Accessed 27 Mar. 2015].
\bibitem{google2x}
A 2x Faster Web. (2009). [online] Chromium Blog. Available at: http://blog.chromium.org/2009/11/2x-faster-web.html [Accessed 20 Feb. 2015].
\bibitem{servy}
Servy, H. (2015). Evaluating the Performance of SPDY-enabled Web Servers. [online] Neotys.com. Available at: http://www.neotys.com/blog/performance-of-spdy-enabled-web-servers/ [Accessed 20 Feb. 2015].
\bibitem{podiatry}
Podiatry, G. (2015). Guy's Pod » Blog Archive » Not as SPDY as You Thought. [online] Guypo.com. Available at: http://www.guypo.com/not-as-spdy-as-you-thought/ [Accessed 20 Feb. 2015].
\bibitem{wang}
Wang et al. (2014). How Speedy is SPDY?, 11th USENIX Symposium on Networked Systems Design and Implementation (NSDI ’14). [online] usenix.org. Available at:
https://www.usenix.org/system/files/conference/nsdi14/nsdi14-paper-wang\_xiao\_sophia.pdf [Accessed 20 Feb. 2015].
\bibitem{amazon} Amazon Elastic Compute Cloud (Amazon EC2) (2015). Available at: http://aws.amazon.com/ec2/ [Accessed 20 Feb. 2015].
\bibitem{http2-imp}  HTTP/2 client/server implemenations (2015). Available at: https://github.com/http2/http2-spec/wiki/Implementations [Accessed 20 Feb. 2015].
\bibitem{h2c-14} Hypertext Transfer Protocol version 2 draft-ietf-httpbis-http2-14 (2014). Available at: https://tools.ietf.org/html/draft-ietf-httpbis-http2-14 [Accessed 4. March 2015]
\bibitem{nghttp} HTTP/2 experimental server (2015). Available at: https://nghttp2.org/documentation/nghttpd.1.html [Accessed 4. March 2015]
\bibitem{apache2} The Apache HTTP Server Project (2015). Available at: http://httpd.apache.org/ [Accessed 4. March 2015]
\bibitem{h2load} Benchmarking tool for HTTP/2 and SPDY server (2015). Available at: https://nghttp2.org/documentation/h2load.1.html [Accessed 4. March 2015]
\bibitem{httparchive} Httparchive.org, (2015). HTTP Archive - Trends. [online] Available at: http://httparchive.org/trends.php [Accessed 11 Mar. 2015].
\bibitem{nginx}
Garrett, O. (2015). How NGINX Plans to Support HTTP/2 - NGINX. [online] NGINX. Available at: http://nginx.com/blog/how-nginx-plans-to-support-http2/ [Accessed 27 Mar. 2015].
\bibitem{amazon-ts} amazon.com, (2015). Amazon - T2 Instances. [online] Available at: http://docs.aws.amazon.com/AWSEC2/latest/UserGuide/t2-instances.html [Accessed 11 Mar. 2015].
\bibitem{nghttpx} nghttp2.org, nghttpx a HTTP/1.1 HTTP/2 reverse proxy. [online] Available at: https://nghttp2.org/documentation/nghttpx.1.html [Accessed 1 April 2015].
\end{thebibliography}